Northern Andes plant species IUCN data

### 2023-02-27 code/L0/L0_Ecuador_plants_IUCN.Rmd
Update for Northern Andes

---
title: "Ecuador plant species IUCN data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "Ecuador_IUCN_plant_species.csv, Ecuador_IUCN_plant_occ.csv, Ecuador_IUCN_plant_habitat.csv"
project: "Frugivoria"
date: "2022-08-31"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

@@

# Ecuador species list
```{r}
#Ecuador
ecuador_species <- rl_sp_country("EC", key = token, parse = TRUE)
ecuador_species <- ecuador_species$result[1]
```

@@

# Generate Ecuador plant species list
```{r}
ecuador_plants <- merge(all_plants, ecuador_species, by="taxonid")
```

# Get occurences for Ecuador using species list
```{r}
get_occ <- function(ID) {
  rl_occ_country<- rl_occ_country(id=ID,key=token)$result
  if (class(rl_occ_country) == 'data.frame') {
    data.frame(taxonid=ID, rl_occ_country)
  } else {
    data.frame(taxonid=ID)
  }
}
ecuador_IUCN_plant_occ <- ecuador_plants %>%
  rowwise %>%
  do(get_occ(.$taxonid))
ecuador_IUCN_plant_occ <- as.data.frame(ecuador_IUCN_plant_occ)
```

# Get habitat for species list
```{r}
get_habitat <- function(ID) {
  habitat_by_sp<- rl_habitats(id=ID,key=token)$result
  if (class(habitat_by_sp) == 'data.frame') {
    data.frame(taxonid=ID, habitat_by_sp)
  } else {
    data.frame(taxonid=ID)
  }
}
ecuador_IUCN_plant_habitat <- ecuador_plants %>%
  rowwise %>%
  do(get_habitat(.$taxonid))
ecuador_IUCN_plant_habitat <- as.data.frame(ecuador_IUCN_plant_habitat)
```

# Summary of data
```{r}
summary(ecuador_plants)
na_summary(ecuador_plants, exclude_cols = c("subpopulation"))
```

```{r}
summary(ecuador_IUCN_plant_occ)
na_summary(ecuador_IUCN_plant_occ)
```

```{r}
summary(ecuador_IUCN_plant_habitat)
na_summary(ecuador_IUCN_plant_habitat)
```

# Write data to csv
```{r}
ecuador_ICUN_species_list_path <- file.path(output_path,"Ecuador_IUCN_plant_species.csv")
write.csv(ecuador_plants, file = ecuador_ICUN_species_list_path)

ecuador_IUCN_plant_occ_path <- file.path(output_path, "Ecuador_IUCN_plant_occ.csv")
write.csv(ecuador_IUCN_plant_occ, file = ecuador_IUCN_plant_occ_path)

ecuador_IUCN_plant_habitat_path <- file.path(output_path, "Ecuador_IUCN_plant_habitat.csv")
write.csv(ecuador_IUCN_plant_habitat, file = ecuador_IUCN_plant_habitat_path)
```

>>>>

---
title: "Northern Andes plant species IUCN data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "NorthAndes_IUCN_plant_species.csv, NorthAndes_IUCN_plant_occ.csv, NorthAndes_IUCN_plant_habitat.csv"
project: "Frugivoria"
date: "2023-02-27"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

@@

# North Andes species list
```{r}
#Ecuador
ecuador_species <- rl_sp_country("EC", key = token, parse = TRUE)
ecuador_species <- ecuador_species$result[1]
#Colombia
colombia_species <- rl_sp_country("CO", key = token, parse = TRUE)
colombia_species <- colombia_species$result[1]
#Venezuela
venezuela_species <- rl_sp_country("VE", key = token, parse = TRUE)
venezuela_species <- venezuela_species$result[1]

#combine all 3
northAndes_species <- rbind(ecuador_species, colombia_species, venezuela_species)
```

@@

# Generate Northern Andes plant species list
```{r}
northAndes_plants <- merge(all_plants, northAndes_species, by="taxonid")
```

# Get occurences for Northern Andes using species list
```{r}
get_occ <- function(ID) {
  rl_occ_country<- rl_occ_country(id=ID,key=token)$result
  if (class(rl_occ_country) == 'data.frame') {
    data.frame(taxonid=ID, rl_occ_country)
  } else {
    data.frame(taxonid=ID)
  }
}
northAndes_IUCN_plant_occ <- northAndes_plants %>%
  rowwise %>%
  do(get_occ(.$taxonid))
northAndes_IUCN_plant_occ <- as.data.frame(northAndes_IUCN_plant_occ)
```

# Get habitat for species list
```{r}
get_habitat <- function(ID) {
  habitat_by_sp<- rl_habitats(id=ID,key=token)$result
  if (class(habitat_by_sp) == 'data.frame') {
    data.frame(taxonid=ID, habitat_by_sp)
  } else {
    data.frame(taxonid=ID)
  }
}
northAndes_IUCN_plant_habitat <- northAndes_plants %>%
  rowwise %>%
  do(get_habitat(.$taxonid))
northAndes_IUCN_plant_habitat <- as.data.frame(northAndes_IUCN_plant_habitat)
```

# Summary of data
```{r}
summary(northAndes_plants)
na_summary(northAndes_plants, exclude_cols = c("subpopulation"))
```

```{r}
summary(northAndes_IUCN_plant_occ)
na_summary(northAndes_IUCN_plant_occ)
```

```{r}
summary(northAndes_IUCN_plant_habitat)
na_summary(northAndes_IUCN_plant_habitat)
```

### using DataExplorer package
```{r}
plot_str(northAndes_plants)
introduce(northAndes_plants)
plot_intro(northAndes_plants)
plot_missing(northAndes_plants)
plot_bar(northAndes_plants)
```

```{r}
plot_str(northAndes_IUCN_plant_occ)
introduce(northAndes_IUCN_plant_occ)
plot_intro(northAndes_IUCN_plant_occ)
plot_missing(northAndes_IUCN_plant_occ)
plot_bar(northAndes_IUCN_plant_occ)
```

```{r}
plot_str(northAndes_IUCN_plant_habitat)
introduce(northAndes_IUCN_plant_habitat)
plot_intro(northAndes_IUCN_plant_habitat)
plot_missing(northAndes_IUCN_plant_habitat)
plot_bar(northAndes_IUCN_plant_habitat)
```

### using summarytools package
```{r}
northAndes_plants_summary <- dfSummary(northAndes_plants, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(northAndes_plants_summary, method = "render")
view(northAndes_plants_summary, file = file.path(output_path,"northAndes_plants_summary.html"))
```

```{r}
northAndes_IUCN_plant_occ_summary <- dfSummary(northAndes_IUCN_plant_occ, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(northAndes_IUCN_plant_occ_summary, method = "render")
view(northAndes_IUCN_plant_occ_summary, file = file.path(output_path,"northAndes_IUCN_plant_occ_summary.html"))
```

```{r}
northAndes_IUCN_plant_habitat_summary <- dfSummary(northAndes_IUCN_plant_habitat, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(northAndes_IUCN_plant_habitat_summary, method = "render")
view(northAndes_IUCN_plant_habitat_summary, file = file.path(output_path,"northAndes_IUCN_plant_habitat_summary.html"))
```

# Write data to csv
```{r}
northAndes_ICUN_species_list_path <- file.path(output_path,"northAndes_IUCN_plant_species.csv")
write.csv(northAndes_plants, file = northAndes_ICUN_species_list_path)

northAndes_IUCN_plant_occ_path <- file.path(output_path, "northAndes_IUCN_plant_occ.csv")
write.csv(northAndes_IUCN_plant_occ, file = northAndes_IUCN_plant_occ_path)

northAndes_IUCN_plant_habitat_path <- file.path(output_path, "northAndes_IUCN_plant_habitat.csv")
write.csv(northAndes_IUCN_plant_habitat, file = northAndes_IUCN_plant_habitat_path)
```
